---
title: "Clean all plant records"
author: "Josie Lesage"
date: "12/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = TRUE)

# Setup packages
library(rgbif)
library(tidyverse)
```

# CCH2 Data

## Cleaning data and removing potential duplicates
The code below should be run after you have downloaded datasets for each of the islands using the spatial/WKT module, and through the terms searches in the CCH2 database.

****
To begin, use ctrl+F to find and *replace all* of the previous dates (for instance, "Dec 2020") with the new date ("Mar 2020").
****


# Term Data
To clean and generate a single data file, we must begin by extracting each zip file to its folder. 
```{r CCH2 unzip}

zipfiles <- list.files("Data/Dec 2020/CCH2/Terms", pattern = "*.zip")

print(zipfiles)

walk(zipfiles, ~ unzip(zipfile = str_c("Data/Dec 2020/CCH2/Terms/", .x),
                       exdir = str_c("Data/Dec 2020/CCH2/Terms/Unzipped/", .x),
                       overwrite = TRUE))
```

Now, we extract the occurrence data for each file and create an object for it.

```{r extract csvs}
Anacapa_I <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Anacapa I.zip/occurrences.csv", col_types = cols(.default = "c"))
Anacapa_Is <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Anacapa Is.zip/occurrences.csv", col_types = cols(.default = "c"))
Anacapa_Isl <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Anacapa Isl.zip/occurrences.csv", col_types = cols(.default = "c"))
Anacapa_Islan <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Anacapa Islan.zip/occurrences.csv", col_types = cols(.default = "c"))
Anacapa_Island <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Anacapa Island.zip/occurrences.csv", col_types = cols(.default = "c"))

Barbara_Isl <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Barbara Isl.zip/occurrences.csv", col_types = cols(.default = "c"))
Barbara_Island <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Barbara Island.zip/occurrences.csv", col_types = cols(.default = "c"))

Benito_Is <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Benito Is.zip/occurrences.csv", col_types = cols(.default = "c"))
Benito_Islan <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Benito Islan.zip/occurrences.csv", col_types = cols(.default = "c"))
Benito_Island <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Benito Island.zip/occurrences.csv", col_types = cols(.default = "c"))

Catalina_I <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Catalina I.zip/occurrences.csv", col_types = cols(.default = "c"))
Catalina_Is <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Catalina Is.zip/occurrences.csv", col_types = cols(.default = "c"))
Catalina_Isl <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Catalina Isl.zip/occurrences.csv", col_types = cols(.default = "c"))
Catalina_Islan <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Catalina Islan.zip/occurrences.csv", col_types = cols(.default = "c"))
Catalina_Island <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Catalina Island.zip/occurrences.csv", col_types = cols(.default = "c"))

Cedros_Is <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Cedros Is.zip/occurrences.csv", col_types = cols(.default = "c"))
Cedros_Isl <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Cedros Isl.zip/occurrences.csv", col_types = cols(.default = "c"))
Cedros_Island <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Cedros Island.zip/occurrences.csv", col_types = cols(.default = "c"))

Clement_Island <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Clement Island.zip/occurrences.csv", col_types = cols(.default = "c"))
Clemente_I <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Clemente I.zip/occurrences.csv", col_types = cols(.default = "c"))
Clemente_Is <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Clemente Is.zip/occurrences.csv", col_types = cols(.default = "c"))
Clemente_Isl <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Clemente Isl.zip/occurrences.csv", col_types = cols(.default = "c"))
Clemente_Island <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Clemente Island.zip/occurrences.csv", col_types = cols(.default = "c"))

Coronado_Isl <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Coronado Isl.zip/occurrences.csv", col_types = cols(.default = "c"))
Coronado_Island <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Coronado Island.zip/occurrences.csv", col_types = cols(.default = "c"))
Coronados_Isl <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Coronados Isl.zip/occurrences.csv", col_types = cols(.default = "c"))
Coronados_Island <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Coronados Island.zip/occurrences.csv", col_types = cols(.default = "c"))

Geronimo_Island <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Geronimo Island.zip/occurrences.csv", col_types = cols(.default = "c"))

Guadalupe_Is <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Guadalupe Is.zip/occurrences.csv", col_types = cols(.default = "c"))
Guadalupe_Isl <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Guadalupe Isl.zip/occurrences.csv", col_types = cols(.default = "c"))
Guadalupe_Island <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Guadalupe Island.zip/occurrences.csv", col_types = cols(.default = "c"))

Isla_Cedros <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Isla Cedros.zip/occurrences.csv", col_types = cols(.default = "c"))
Isla_Coronado <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Isla Coronado.zip/occurrences.csv", col_types = cols(.default = "c"))
Isla_de_Cedros <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Isla de Cedros.zip/occurrences.csv", col_types = cols(.default = "c"))
Isla_Geronimo <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Isla Geronimo.zip/occurrences.csv", col_types = cols(.default = "c"))
Isla_Guadalupe <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Isla Guadalupe.zip/occurrences.csv", col_types = cols(.default = "c"))
Isla_Natividad <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Isla Natividad.zip/occurrences.csv", col_types = cols(.default = "c"))
Isla_San_Benito <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Isla San Benito.zip/occurrences.csv", col_types = cols(.default = "c"))
Isla_San_Geronimo <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Isla San Geronimo.zip/occurrences.csv", col_types = cols(.default = "c"))
Isla_San_Martin <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Isla San Martin.zip/occurrences.csv", col_types = cols(.default = "c"))
Isla_Todos_Santos <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Isla Todos Santos.zip/occurrences.csv", col_types = cols(.default = "c"))
Islas_de_Todos_Santos <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Islas de Todos Santos.zip/occurrences.csv", col_types = cols(.default = "c"))
Islas_San_Benito <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Islas San Benito.zip/occurrences.csv", col_types = cols(.default = "c"))
Islas_Todos_Santos <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Islas Todos Santos.zip/occurrences.csv", col_types = cols(.default = "c"))

Jeronimo_Island <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Jeronimo Island.zip/occurrences.csv", col_types = cols(.default = "c"))

Martin_Is <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Martin Is.zip/occurrences.csv", col_types = cols(.default = "c"))
Martin_Island <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Martin Island.zip/occurrences.csv", col_types = cols(.default = "c"))

Miguel_I <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Miguel I.zip/occurrences.csv", col_types = cols(.default = "c"))
Miguel_Is <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Miguel Is.zip/occurrences.csv", col_types = cols(.default = "c"))
Miguel_Isl <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Miguel Isl.zip/occurrences.csv", col_types = cols(.default = "c"))
Miguel_Islan <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Miguel Islan.zip/occurrences.csv", col_types = cols(.default = "c"))
Miguel_Island <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Miguel Island.zip/occurrences.csv", col_types = cols(.default = "c"))

Natividad_Is <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Natividad Is.zip/occurrences.csv", col_types = cols(.default = "c"))
Natividad_Isl <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Natividad Isl.zip/occurrences.csv", col_types = cols(.default = "c"))
Natividad_Island <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Natividad Island.zip/occurrences.csv", col_types = cols(.default = "c"))

Nicholas_Isl <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Nicholas Isl.zip/occurrences.csv", col_types = cols(.default = "c"))
Nicholas_Island <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Nicholas Island.zip/occurrences.csv", col_types = cols(.default = "c"))
Nicolas_I <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Nicolas I.zip/occurrences.csv", col_types = cols(.default = "c"))
Nicolas_Isl <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Nicolas Isl.zip/occurrences.csv", col_types = cols(.default = "c"))
Nicolas_Islan <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Nicolas Islan.zip/occurrences.csv", col_types = cols(.default = "c"))
Nicolas_Island <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Nicolas Island.zip/occurrences.csv", col_types = cols(.default = "c"))

San_Martin_I <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/San Martin I.zip/occurrences.csv", col_types = cols(.default = "c"))

Santa_Cruz_I <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Santa Cruz I.zip/occurrences.csv", col_types = cols(.default = "c"))
Santa_Cruz_Is <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Santa Cruz Is.zip/occurrences.csv", col_types = cols(.default = "c"))
Santa_Cruz_Isl <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Santa Cruz Isl.zip/occurrences.csv", col_types = cols(.default = "c"))
Santa_Cruz_Island <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Santa Cruz Island.zip/occurrences.csv", col_types = cols(.default = "c"))

Santa_Rosa_I <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Santa Rosa I.zip/occurrences.csv", col_types = cols(.default = "c"))
Santa_Rosa_Is  <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Santa Rosa Is.zip/occurrences.csv", col_types = cols(.default = "c"))
Santa_Rosa_Isl <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Santa Rosa Isl.zip/occurrences.csv", col_types = cols(.default = "c"))
Santa_Rosa_Island <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Santa Rosa Island.zip/occurrences.csv", col_types = cols(.default = "c"))

Todo_Santos_Island <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Todo Santos Island.zip/occurrences.csv", col_types = cols(.default = "c"))
Todos_Santos_del <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Todos Santos del.zip/occurrences.csv", col_types = cols(.default = "c"))
Todos_Santos_Island <- read_csv("Data/Dec 2020/CCH2/Terms/Unzipped/Todos Santos Island.zip/occurrences.csv", col_types = cols(.default = "c"))

```


Now, we want to join all of the datasets into one big one.

```{r glue terms}
cch2_terms <- full_join(Anacapa_I, Anacapa_Is)
cch2_terms <- full_join(cch2_terms, Anacapa_Isl)
cch2_terms <- full_join(cch2_terms, Anacapa_Islan)
cch2_terms <- full_join(cch2_terms, Anacapa_Island)

cch2_terms <- full_join(cch2_terms, Barbara_Isl)
cch2_terms <- full_join(cch2_terms, Barbara_Island)

cch2_terms <- full_join(cch2_terms, Benito_Isl)
cch2_terms <- full_join(cch2_terms, Benito_Islan)
cch2_terms <- full_join(cch2_terms, Benito_Island)

cch2_terms <- full_join(cch2_terms, Catalina_I)
cch2_terms <- full_join(cch2_terms, Catalina_Is)
cch2_terms <- full_join(cch2_terms, Catalina_Isl)
cch2_terms <- full_join(cch2_terms, Catalina_Islan)
cch2_terms <- full_join(cch2_terms, Catalina_Island)

cch2_terms <- full_join(cch2_terms, Cedros_Is)
cch2_terms <- full_join(cch2_terms, Cedros_Isl)
cch2_terms <- full_join(cch2_terms, Cedros_Island)

cch2_terms <- full_join(cch2_terms, Clement_Island)
cch2_terms <- full_join(cch2_terms, Clemente_I)
cch2_terms <- full_join(cch2_terms, Clemente_Is)
cch2_terms <- full_join(cch2_terms, Clemente_Isl)
cch2_terms <- full_join(cch2_terms, Clemente_Island)

cch2_terms <- full_join(cch2_terms, Coronado_Isl)
cch2_terms <- full_join(cch2_terms, Coronado_Island)
cch2_terms <- full_join(cch2_terms, Coronados_Isl)
cch2_terms <- full_join(cch2_terms, Coronados_Island)

cch2_terms <- full_join(cch2_terms, Geronimo_Island)

cch2_terms <- full_join(cch2_terms, Guadalupe_Is)
cch2_terms <- full_join(cch2_terms, Guadalupe_Isl)
cch2_terms <- full_join(cch2_terms, Guadalupe_Island)

cch2_terms <- full_join(cch2_terms, Isla_Cedros)
cch2_terms <- full_join(cch2_terms, Isla_Coronado)
cch2_terms <- full_join(cch2_terms, Isla_de_Cedros)
cch2_terms <- full_join(cch2_terms, Isla_Geronimo)
cch2_terms <- full_join(cch2_terms, Isla_Guadalupe)
cch2_terms <- full_join(cch2_terms, Isla_Natividad)
cch2_terms <- full_join(cch2_terms, Isla_San_Benito)
cch2_terms <- full_join(cch2_terms, Isla_San_Geronimo)
cch2_terms <- full_join(cch2_terms, Isla_San_Martin)
cch2_terms <- full_join(cch2_terms, Isla_Todos_Santos)
cch2_terms <- full_join(cch2_terms, Islas_de_Todos_Santos)
cch2_terms <- full_join(cch2_terms, Islas_San_Benito)
cch2_terms <- full_join(cch2_terms, Islas_Todos_Santos)

cch2_terms <- full_join(cch2_terms, Jeronimo_Island)

cch2_terms <- full_join(cch2_terms, Martin_Is)
cch2_terms <- full_join(cch2_terms, Martin_Island)

cch2_terms <- full_join(cch2_terms, Miguel_I)
cch2_terms <- full_join(cch2_terms, Miguel_Is)
cch2_terms <- full_join(cch2_terms, Miguel_Isl)
cch2_terms <- full_join(cch2_terms, Miguel_Islan)
cch2_terms <- full_join(cch2_terms, Miguel_Island)

cch2_terms <- full_join(cch2_terms, Natividad_Is)
cch2_terms <- full_join(cch2_terms, Natividad_Isl)
cch2_terms <- full_join(cch2_terms, Natividad_Island)

cch2_terms <- full_join(cch2_terms, Nicholas_Isl)
cch2_terms <- full_join(cch2_terms, Nicholas_Island)
cch2_terms <- full_join(cch2_terms, Nicolas_I)
cch2_terms <- full_join(cch2_terms, Nicolas_Isl)
cch2_terms <- full_join(cch2_terms, Nicolas_Islan)
cch2_terms <- full_join(cch2_terms, Nicolas_Island)

cch2_terms <- full_join(cch2_terms, San_Martin_I)

cch2_terms <- full_join(cch2_terms, Santa_Cruz_I)
cch2_terms <- full_join(cch2_terms, Santa_Cruz_Is)
cch2_terms <- full_join(cch2_terms, Santa_Cruz_Isl)
cch2_terms <- full_join(cch2_terms, Santa_Cruz_Island)

cch2_terms <- full_join(cch2_terms, Santa_Rosa_I)
cch2_terms <- full_join(cch2_terms, Santa_Rosa_Is)
cch2_terms <- full_join(cch2_terms, Santa_Rosa_Isl)
cch2_terms <- full_join(cch2_terms, Santa_Rosa_Island)

cch2_terms <- full_join(cch2_terms, Todo_Santos_Island)
cch2_terms <- full_join(cch2_terms, Todos_Santos_del)
cch2_terms <- full_join(cch2_terms, Todos_Santos_Island)
```

Voila, "cch2_terms" is a huge dataset and has everyone (but probably some dupes). 

# Spatial/WKT data

There are fewer WKT datasets, but we need to extact and glue them too. 
```{r unzip WKTs}
unzip("Data/Dec 2020/CCH2/WKTs/Barbara.zip", exdir = "Data/Dec 2020/CCH2/WKTs/Barbara")
unzip("Data/Dec 2020/CCH2/WKTs/Benito.zip", exdir = "Data/Dec 2020/CCH2/WKTs/Benito")
unzip("Data/Dec 2020/CCH2/WKTs/Catalina.zip", exdir = "Data/Dec 2020/CCH2/WKTs/Catalina")
unzip("Data/Dec 2020/CCH2/WKTs/Clemente.zip", exdir = "Data/Dec 2020/CCH2/WKTs/Clemente")
unzip("Data/Dec 2020/CCH2/WKTs/Coronados.zip", exdir = "Data/Dec 2020/CCH2/WKTs/Coronados")
unzip("Data/Dec 2020/CCH2/WKTs/Geronimo.zip", exdir = "Data/Dec 2020/CCH2/WKTs/Geronimo")
unzip("Data/Dec 2020/CCH2/WKTs/Guadalupe.zip", exdir = "Data/Dec 2020/CCH2/WKTs/Guadalupe")
unzip("Data/Dec 2020/CCH2/WKTs/Martin.zip", exdir = "Data/Dec 2020/CCH2/WKTs/Martin")
unzip("Data/Dec 2020/CCH2/WKTs/Miguel_Rosa_Cruz.zip", exdir = "Data/Dec 2020/CCH2/WKTs/Miguel_Rosa_Cruz")
unzip("Data/Dec 2020/CCH2/WKTs/Natividad_Cedros.zip", exdir = "Data/Dec 2020/CCH2/WKTs/Natividad_Cedros")
unzip("Data/Dec 2020/CCH2/WKTs/Nicolas.zip", exdir = "Data/Dec 2020/CCH2/WKTs/Nicolas")
unzip("Data/Dec 2020/CCH2/WKTs/Todos_Santos.zip", exdir = "Data/Dec 2020/CCH2/WKTs/Todos_Santos")
```

```{r import WKTs}
Barbara_WKT <- read_csv("Data/Dec 2020/CCH2/WKTs/Barbara/occurrences.csv", col_types = cols(.default = "c"))
Benito_WKT <- read_csv("Data/Dec 2020/CCH2/WKTs/Benito/occurrences.csv", col_types = cols(.default = "c"))
Catalina_WKT <- read_csv("Data/Dec 2020/CCH2/WKTs/Catalina/occurrences.csv", col_types = cols(.default = "c"))
Clemente_WKT <- read_csv("Data/Dec 2020/CCH2/WKTs/Clemente/occurrences.csv", col_types = cols(.default = "c"))
Coronados_WKT <- read_csv("Data/Dec 2020/CCH2/WKTs/Coronados/occurrences.csv", col_types = cols(.default = "c"))
Geronimo_WKT <- read_csv("Data/Dec 2020/CCH2/WKTs/Geronimo/occurrences.csv", col_types = cols(.default = "c"))
Guadalupe_WKT <- read_csv("Data/Dec 2020/CCH2/WKTs/Guadalupe/occurrences.csv", col_types = cols(.default = "c"))
Martin_WKT <- read_csv("Data/Dec 2020/CCH2/WKTs/Martin/occurrences.csv", col_types = cols(.default = "c"))
Miguel_Rosa_Cruz_WKT <- read_csv("Data/Dec 2020/CCH2/WKTs/Miguel_Rosa_Cruz/occurrences.csv", col_types = cols(.default = "c"))
Natividad_Cedros_WKT <- read_csv("Data/Dec 2020/CCH2/WKTs/Natividad_Cedros/occurrences.csv", col_types = cols(.default = "c"))
Nicolas_WKT <- read_csv("Data/Dec 2020/CCH2/WKTs/Nicolas/occurrences.csv", col_types = cols(.default = "c"))
Todos_Santos_WKT <- read_csv("Data/Dec 2020/CCH2/WKTs/Todos_Santos/occurrences.csv", col_types = cols(.default = "c"))
```

```{r glue WKTs}
cch2_wkts <- full_join(Barbara_WKT, Benito_WKT)
cch2_wkts <- full_join(cch2_wkts, Catalina_WKT)
cch2_wkts <- full_join(cch2_wkts, Clemente_WKT)
cch2_wkts <- full_join(cch2_wkts, Coronados_WKT)
cch2_wkts <- full_join(cch2_wkts, Geronimo_WKT)
cch2_wkts <- full_join(cch2_wkts, Guadalupe_WKT)
cch2_wkts <- full_join(cch2_wkts, Martin_WKT)
cch2_wkts <- full_join(cch2_wkts, Miguel_Rosa_Cruz_WKT)
cch2_wkts <- full_join(cch2_wkts, Natividad_Cedros_WKT)
cch2_wkts <- full_join(cch2_wkts, Nicolas_WKT)
cch2_wkts <- full_join(cch2_wkts, Todos_Santos_WKT)
```

# The final gluing

Now that we have both a CCH2 term and a CCH2 WKT dataset, we need to remove as many duplicates as we possibly can. 

```{r dupe clear}
cch2_all <- full_join(cch2_terms, cch2_wkts)
cch2_all_dist <- distinct(cch2_all, id, .keep_all = TRUE)
cch2_all_dist_2 <- distinct(cch2_all_dist, occurrenceID, .keep_all = TRUE)

write.csv(cch2_all_dist_2, file = "Data/Dec 2020/CCH2/CCH_Clean.csv", na="", row.names=FALSE)
```

