---
title: "Step4_SEINetCleanup"
author: "Josie Lesage"
date: "12/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = TRUE)

# Setup packages
library(tidyverse)
```

# SEINet Data

## Cleaning data and removing potential duplicates
The code below should be run after you have downloaded datasets for each of the islands, and the special terms searches, in both the seinet and SEINet databases.

****
To begin, use ctrl+F to find and *replace all* of the previous dates (for instance, "Dec 2020") with the new date ("Mar 2020").
****


# Term Data
To clean and generate a single data file, we must begin by extracting each zip file to its folder. 

```{r seinet unzip}
unzip("Data/Dec 2020/SEINet/Terms/Anacapa Island.zip", exdir = "Data/Dec 2020/SEINet/Terms/Anacapa Island")

unzip("Data/Dec 2020/SEINet/Terms/Barbara Isl.zip", exdir = "Data/Dec 2020/SEINet/Terms/Barbara Isl")
unzip("Data/Dec 2020/SEINet/Terms/Barbara Island.zip", exdir = "Data/Dec 2020/SEINet/Terms/Barbara Island")

unzip("Data/Dec 2020/SEINet/Terms/Benito Is.zip", exdir = "Data/Dec 2020/SEINet/Terms/Benito Is")
unzip("Data/Dec 2020/SEINet/Terms/Benito Island.zip", exdir = "Data/Dec 2020/SEINet/Terms/Benito Island")

unzip("Data/Dec 2020/SEINet/Terms/Catalina I.zip", exdir = "Data/Dec 2020/SEINet/Terms/Catalina I")
unzip("Data/Dec 2020/SEINet/Terms/Catalina Is.zip", exdir = "Data/Dec 2020/SEINet/Terms/Catalina Is")
unzip("Data/Dec 2020/SEINet/Terms/Catalina Isl.zip", exdir = "Data/Dec 2020/SEINet/Terms/Catalina Isl")
unzip("Data/Dec 2020/SEINet/Terms/Catalina Islan.zip", exdir = "Data/Dec 2020/SEINet/Terms/Catalina Islan")
unzip("Data/Dec 2020/SEINet/Terms/Catalina Island.zip", exdir = "Data/Dec 2020/SEINet/Terms/Catalina Island")


unzip("Data/Dec 2020/SEINet/Terms/Cedros Is.zip", exdir = "Data/Dec 2020/SEINet/Terms/Cedros Is")
unzip("Data/Dec 2020/SEINet/Terms/Cedros Islan.zip", exdir = "Data/Dec 2020/SEINet/Terms/Cedros Islan")
unzip("Data/Dec 2020/SEINet/Terms/Cedros Island.zip", exdir = "Data/Dec 2020/SEINet/Terms/Cedros Island")

unzip("Data/Dec 2020/SEINet/Terms/Clement Island.zip", exdir = "Data/Dec 2020/SEINet/Terms/Clement Island")
unzip("Data/Dec 2020/SEINet/Terms/Clemente Is.zip", exdir = "Data/Dec 2020/SEINet/Terms/Clemente Is")
unzip("Data/Dec 2020/SEINet/Terms/Clemente Isl.zip", exdir = "Data/Dec 2020/SEINet/Terms/Clemente Isl")
unzip("Data/Dec 2020/SEINet/Terms/Clemente Island.zip", exdir = "Data/Dec 2020/SEINet/Terms/Clemente Island")

unzip("Data/Dec 2020/SEINet/Terms/Coronado Is.zip", exdir = "Data/Dec 2020/SEINet/Terms/Coronado Is")
unzip("Data/Dec 2020/SEINet/Terms/Coronado Isl.zip", exdir = "Data/Dec 2020/SEINet/Terms/Coronado Isl")
unzip("Data/Dec 2020/SEINet/Terms/Coronado Island.zip", exdir = "Data/Dec 2020/SEINet/Terms/Coronado Island")
unzip("Data/Dec 2020/SEINet/Terms/Coronados Isl.zip", exdir = "Data/Dec 2020/SEINet/Terms/Coronados Isl")
unzip("Data/Dec 2020/SEINet/Terms/Coronados Island.zip", exdir = "Data/Dec 2020/SEINet/Terms/Coronados Island")

unzip("Data/Dec 2020/SEINet/Terms/Geronimo Island.zip", exdir = "Data/Dec 2020/SEINet/Terms/Geronimo Island")

unzip("Data/Dec 2020/SEINet/Terms/Guadalupe I.zip", exdir = "Data/Dec 2020/SEINet/Terms/Guadalupe I")
unzip("Data/Dec 2020/SEINet/Terms/Guadalupe Is.zip", exdir = "Data/Dec 2020/SEINet/Terms/Guadalupe Is")
unzip("Data/Dec 2020/SEINet/Terms/Guadalupe Island.zip", exdir = "Data/Dec 2020/SEINet/Terms/Guadalupe Island")

unzip("Data/Dec 2020/SEINet/Terms/Isla Cedros.zip", exdir = "Data/Dec 2020/SEINet/Terms/Isla Cedros")
unzip("Data/Dec 2020/SEINet/Terms/Isla Coronado.zip", exdir = "Data/Dec 2020/SEINet/Terms/Isla Coronado")
unzip("Data/Dec 2020/SEINet/Terms/Isla de Cedros.zip", exdir = "Data/Dec 2020/SEINet/Terms/Isla de Cedros")
unzip("Data/Dec 2020/SEINet/Terms/Isla Guadalupe.zip", exdir = "Data/Dec 2020/SEINet/Terms/Isla Guadalupe")
unzip("Data/Dec 2020/SEINet/Terms/Isla Natividad.zip", exdir = "Data/Dec 2020/SEINet/Terms/Isla Natividad")
unzip("Data/Dec 2020/SEINet/Terms/Isla San Benito.zip", exdir = "Data/Dec 2020/SEINet/Terms/Isla San Benito")
unzip("Data/Dec 2020/SEINet/Terms/Isla San Martin.zip", exdir = "Data/Dec 2020/SEINet/Terms/Isla San Martin")
unzip("Data/Dec 2020/SEINet/Terms/Isla Todos Santos.zip", exdir = "Data/Dec 2020/SEINet/Terms/Isla Todos Santos")
unzip("Data/Dec 2020/SEINet/Terms/Islas de Todos Santos.zip", exdir = "Data/Dec 2020/SEINet/Terms/Islas de Todos Santos")
unzip("Data/Dec 2020/SEINet/Terms/Islas San Benito.zip", exdir = "Data/Dec 2020/SEINet/Terms/Islas San Benito")
unzip("Data/Dec 2020/SEINet/Terms/Islas Todos Santos.zip", exdir = "Data/Dec 2020/SEINet/Terms/Islas Todos Santos")

unzip("Data/Dec 2020/SEINet/Terms/Jeronimo Island.zip", exdir = "Data/Dec 2020/SEINet/Terms/Jeronimo Island")

unzip("Data/Dec 2020/SEINet/Terms/Martin I.zip", exdir = "Data/Dec 2020/SEINet/Terms/Martin I")
unzip("Data/Dec 2020/SEINet/Terms/Martin Island.zip", exdir = "Data/Dec 2020/SEINet/Terms/Martin Island")

unzip("Data/Dec 2020/SEINet/Terms/Miguel Is.zip", exdir = "Data/Dec 2020/SEINet/Terms/Miguel Is")
unzip("Data/Dec 2020/SEINet/Terms/Miguel Island.zip", exdir = "Data/Dec 2020/SEINet/Terms/Miguel Island")

unzip("Data/Dec 2020/SEINet/Terms/Natividad Island.zip", exdir = "Data/Dec 2020/SEINet/Terms/Natividad Island")

unzip("Data/Dec 2020/SEINet/Terms/Nicholas Island.zip", exdir = "Data/Dec 2020/SEINet/Terms/Nicholas Island")
unzip("Data/Dec 2020/SEINet/Terms/Nicolas I.zip", exdir = "Data/Dec 2020/SEINet/Terms/Nicolas I")
unzip("Data/Dec 2020/SEINet/Terms/Nicolas Island.zip", exdir = "Data/Dec 2020/SEINet/Terms/Nicolas Island")

unzip("Data/Dec 2020/SEINet/Terms/Santa Cruz I.zip", exdir = "Data/Dec 2020/SEINet/Terms/Santa Cruz I")
unzip("Data/Dec 2020/SEINet/Terms/Santa Cruz Is.zip", exdir = "Data/Dec 2020/SEINet/Terms/Santa Cruz Is")
unzip("Data/Dec 2020/SEINet/Terms/Santa Cruz Isl.zip", exdir = "Data/Dec 2020/SEINet/Terms/Santa Cruz Isl")
unzip("Data/Dec 2020/SEINet/Terms/Santa Cruz Islan.zip", exdir = "Data/Dec 2020/SEINet/Terms/Santa Cruz Islan")
unzip("Data/Dec 2020/SEINet/Terms/Santa Cruz Island.zip", exdir = "Data/Dec 2020/SEINet/Terms/Santa Cruz Island")

unzip("Data/Dec 2020/SEINet/Terms/Santa Rosa I.zip", exdir = "Data/Dec 2020/SEINet/Terms/Santa Rosa I")
unzip("Data/Dec 2020/SEINet/Terms/Santa Rosa Is.zip", exdir = "Data/Dec 2020/SEINet/Terms/Santa Rosa Is")
unzip("Data/Dec 2020/SEINet/Terms/Santa Rosa Isl.zip", exdir = "Data/Dec 2020/SEINet/Terms/Santa Rosa Isl")
unzip("Data/Dec 2020/SEINet/Terms/Santa Rosa Island.zip", exdir = "Data/Dec 2020/SEINet/Terms/Santa Rosa Island")

unzip("Data/Dec 2020/SEINet/Terms/Todos Santos del.zip", exdir = "Data/Dec 2020/SEINet/Terms/Todos Santos del")
unzip("Data/Dec 2020/SEINet/Terms/Todos Santos Island.zip", exdir = "Data/Dec 2020/SEINet/Terms/Todos Santos Island")
```


After unzipping, we'll import into R.

```{r extract csvs}
Anacapa_Island <- read_csv("Data/Dec 2020/SEINet/Terms/Anacapa Island/occurrences.csv", col_types = cols(.default = "c"))

Barbara_Isl <- read_csv("Data/Dec 2020/SEINet/Terms/Barbara Isl/occurrences.csv", col_types = cols(.default = "c"))
Barbara_Island <- read_csv("Data/Dec 2020/SEINet/Terms/Barbara Island/occurrences.csv", col_types = cols(.default = "c"))

Benito_Is <- read_csv("Data/Dec 2020/SEINet/Terms/Benito Is/occurrences.csv", col_types = cols(.default = "c"))
Benito_Island <- read_csv("Data/Dec 2020/SEINet/Terms/Benito Island/occurrences.csv", col_types = cols(.default = "c"))

Catalina_I <- read_csv("Data/Dec 2020/SEINet/Terms/Catalina I/occurrences.csv", col_types = cols(.default = "c"))
Catalina_Is <- read_csv("Data/Dec 2020/SEINet/Terms/Catalina Is/occurrences.csv", col_types = cols(.default = "c"))
Catalina_Isl <- read_csv("Data/Dec 2020/SEINet/Terms/Catalina Isl/occurrences.csv", col_types = cols(.default = "c"))
Catalina_Islan <- read_csv("Data/Dec 2020/SEINet/Terms/Catalina Islan/occurrences.csv", col_types = cols(.default = "c"))
Catalina_Island <- read_csv("Data/Dec 2020/SEINet/Terms/Catalina Island/occurrences.csv", col_types = cols(.default = "c"))

Cedros_Is <- read_csv("Data/Dec 2020/SEINet/Terms/Cedros Is/occurrences.csv", col_types = cols(.default = "c"))
Cedros_Islan <- read_csv("Data/Dec 2020/SEINet/Terms/Cedros Islan/occurrences.csv", col_types = cols(.default = "c"))
Cedros_Island <- read_csv("Data/Dec 2020/SEINet/Terms/Cedros Island/occurrences.csv", col_types = cols(.default = "c"))

Clement_Island <- read_csv("Data/Dec 2020/SEINet/Terms/Clement Island/occurrences.csv", col_types = cols(.default = "c"))
Clemente_Is <- read_csv("Data/Dec 2020/SEINet/Terms/Clemente Is/occurrences.csv", col_types = cols(.default = "c"))
Clemente_Isl <- read_csv("Data/Dec 2020/SEINet/Terms/Clemente Isl/occurrences.csv", col_types = cols(.default = "c"))
Clemente_Island <- read_csv("Data/Dec 2020/SEINet/Terms/Clemente Island/occurrences.csv", col_types = cols(.default = "c"))

Coronado_Is <- read_csv("Data/Dec 2020/SEINet/Terms/Coronado Is/occurrences.csv", col_types = cols(.default = "c"))
Coronado_Isl <- read_csv("Data/Dec 2020/SEINet/Terms/Coronado Isl/occurrences.csv", col_types = cols(.default = "c"))
Coronado_Island <- read_csv("Data/Dec 2020/SEINet/Terms/Coronado Island/occurrences.csv", col_types = cols(.default = "c"))
Coronados_Isl <- read_csv("Data/Dec 2020/SEINet/Terms/Coronados Isl/occurrences.csv", col_types = cols(.default = "c"))
Coronados_Island <- read_csv("Data/Dec 2020/SEINet/Terms/Coronados Island/occurrences.csv", col_types = cols(.default = "c"))

Geronimo_Island <- read_csv("Data/Dec 2020/SEINet/Terms/Geronimo Island/occurrences.csv", col_types = cols(.default = "c"))

Guadalupe_I <- read_csv("Data/Dec 2020/SEINet/Terms/Guadalupe I/occurrences.csv", col_types = cols(.default = "c"))
Guadalupe_Is <- read_csv("Data/Dec 2020/SEINet/Terms/Guadalupe Is/occurrences.csv", col_types = cols(.default = "c"))
Guadalupe_Island <- read_csv("Data/Dec 2020/SEINet/Terms/Guadalupe Island/occurrences.csv", col_types = cols(.default = "c"))

Isla_Cedros <- read_csv("Data/Dec 2020/SEINet/Terms/Isla Cedros/occurrences.csv", col_types = cols(.default = "c"))
Isla_Coronado <- read_csv("Data/Dec 2020/SEINet/Terms/Isla Coronado/occurrences.csv", col_types = cols(.default = "c"))
Isla_de_Cedros <- read_csv("Data/Dec 2020/SEINet/Terms/Isla de Cedros/occurrences.csv", col_types = cols(.default = "c"))
Isla_Guadalupe <- read_csv("Data/Dec 2020/SEINet/Terms/Isla Guadalupe/occurrences.csv", col_types = cols(.default = "c"))
Isla_Natividad <- read_csv("Data/Dec 2020/SEINet/Terms/Isla Natividad/occurrences.csv", col_types = cols(.default = "c"))
Isla_San_Benito <- read_csv("Data/Dec 2020/SEINet/Terms/Isla San Benito/occurrences.csv", col_types = cols(.default = "c"))
Isla_San_Martin <- read_csv("Data/Dec 2020/SEINet/Terms/Isla San Martin/occurrences.csv", col_types = cols(.default = "c"))
Isla_Todos_Santos  <- read_csv("Data/Dec 2020/SEINet/Terms/Isla Todos Santos/occurrences.csv", col_types = cols(.default = "c"))
Islas_de_Todos_Santos <- read_csv("Data/Dec 2020/SEINet/Terms/Islas de Todos Santos/occurrences.csv", col_types = cols(.default = "c"))
Islas_San_Benito <- read_csv("Data/Dec 2020/SEINet/Terms/Islas San Benito/occurrences.csv", col_types = cols(.default = "c"))
Islas_Todos_Santos <- read_csv("Data/Dec 2020/SEINet/Terms/Islas Todos Santos/occurrences.csv", col_types = cols(.default = "c"))

Jeronimo_Island <- read_csv("Data/Dec 2020/SEINet/Terms/Jeronimo Island/occurrences.csv", col_types = cols(.default = "c"))

Martin_I <- read_csv("Data/Dec 2020/SEINet/Terms/Martin I/occurrences.csv", col_types = cols(.default = "c"))
Martin_Island <- read_csv("Data/Dec 2020/SEINet/Terms/Martin Island/occurrences.csv", col_types = cols(.default = "c"))

Miguel_Is <- read_csv("Data/Dec 2020/SEINet/Terms/Miguel Is/occurrences.csv", col_types = cols(.default = "c"))
Miguel_Island <- read_csv("Data/Dec 2020/SEINet/Terms/Miguel Island/occurrences.csv", col_types = cols(.default = "c"))

Natividad_Island <- read_csv("Data/Dec 2020/SEINet/Terms/Natividad Island/occurrences.csv", col_types = cols(.default = "c"))

Nicholas_Island <- read_csv("Data/Dec 2020/SEINet/Terms/Nicholas Island/occurrences.csv", col_types = cols(.default = "c"))
Nicolas_I <- read_csv("Data/Dec 2020/SEINet/Terms/Nicolas I/occurrences.csv", col_types = cols(.default = "c"))
Nicolas_Island <- read_csv("Data/Dec 2020/SEINet/Terms/Nicolas Island/occurrences.csv", col_types = cols(.default = "c"))

Santa_Cruz_I <- read_csv("Data/Dec 2020/SEINet/Terms/Santa Cruz I/occurrences.csv", col_types = cols(.default = "c"))
Santa_Cruz_Is <- read_csv("Data/Dec 2020/SEINet/Terms/Santa Cruz Is/occurrences.csv", col_types = cols(.default = "c"))
Santa_Cruz_Isl <- read_csv("Data/Dec 2020/SEINet/Terms/Santa Cruz Isl/occurrences.csv", col_types = cols(.default = "c"))
Santa_Cruz_Islan <- read_csv("Data/Dec 2020/SEINet/Terms/Santa Cruz Islan/occurrences.csv", col_types = cols(.default = "c"))
Santa_Cruz_Island <- read_csv("Data/Dec 2020/SEINet/Terms/Santa Cruz Island/occurrences.csv", col_types = cols(.default = "c"))

Santa_Rosa_I <- read_csv("Data/Dec 2020/SEINet/Terms/Santa Rosa I/occurrences.csv", col_types = cols(.default = "c"))
Santa_Rosa_Is <- read_csv("Data/Dec 2020/SEINet/Terms/Santa Rosa Isl/occurrences.csv", col_types = cols(.default = "c"))
Santa_Rosa_Isl <- read_csv("Data/Dec 2020/SEINet/Terms/Santa Rosa Isl/occurrences.csv", col_types = cols(.default = "c"))
Santa_Rosa_Island <- read_csv("Data/Dec 2020/SEINet/Terms/Santa Rosa Island/occurrences.csv", col_types = cols(.default = "c"))

Todos_Santos_del <- read_csv("Data/Dec 2020/SEINet/Terms/Todos Santos del/occurrences.csv", col_types = cols(.default = "c"))
Todos_Santos_Island <- read_csv("Data/Dec 2020/SEINet/Terms/Todos Santos Island/occurrences.csv", col_types = cols(.default = "c"))
```

Now, we want to join all of the terms datasets into one big one.

```{r glue terms}
seinet_terms <- full_join(Anacapa_Island, Barbara_Isl)
seinet_terms <- full_join(seinet_terms, Barbara_Island)

seinet_terms <- full_join(seinet_terms, Benito_Is)
seinet_terms <- full_join(seinet_terms, Benito_Island)

seinet_terms <- full_join(seinet_terms, Catalina_I)
seinet_terms <- full_join(seinet_terms, Catalina_Is)
seinet_terms <- full_join(seinet_terms, Catalina_Isl)
seinet_terms <- full_join(seinet_terms, Catalina_Islan)
seinet_terms <- full_join(seinet_terms, Catalina_Island)

seinet_terms <- full_join(seinet_terms, Cedros_Is)
seinet_terms <- full_join(seinet_terms, Cedros_Islan)
seinet_terms <- full_join(seinet_terms, Cedros_Island)

seinet_terms <- full_join(seinet_terms, Clement_Island)
seinet_terms <- full_join(seinet_terms, Clemente_Is)
seinet_terms <- full_join(seinet_terms, Clemente_Isl)
seinet_terms <- full_join(seinet_terms, Clemente_Island)

seinet_terms <- full_join(seinet_terms, Coronado_Is)
seinet_terms <- full_join(seinet_terms, Coronado_Isl)
seinet_terms <- full_join(seinet_terms, Coronado_Island)
seinet_terms <- full_join(seinet_terms, Coronados_Isl)
seinet_terms <- full_join(seinet_terms, Coronados_Island)

seinet_terms <- full_join(seinet_terms, Geronimo_Island)

seinet_terms <- full_join(seinet_terms, Guadalupe_I)
seinet_terms <- full_join(seinet_terms, Guadalupe_Is)
seinet_terms <- full_join(seinet_terms, Guadalupe_Island)

seinet_terms <- full_join(seinet_terms, Isla_Cedros)
seinet_terms <- full_join(seinet_terms, Isla_Coronado)
seinet_terms <- full_join(seinet_terms, Isla_de_Cedros)
seinet_terms <- full_join(seinet_terms, Isla_Guadalupe)
seinet_terms <- full_join(seinet_terms, Isla_Natividad)
seinet_terms <- full_join(seinet_terms, Isla_San_Benito)
seinet_terms <- full_join(seinet_terms, Isla_San_Martin)
seinet_terms <- full_join(seinet_terms, Isla_Todos_Santos)
seinet_terms <- full_join(seinet_terms, Islas_de_Todos_Santos)
seinet_terms <- full_join(seinet_terms, Islas_San_Benito)
seinet_terms <- full_join(seinet_terms, Islas_Todos_Santos)

seinet_terms <- full_join(seinet_terms, Jeronimo_Island)

seinet_terms <- full_join(seinet_terms, Martin_I)
seinet_terms <- full_join(seinet_terms, Martin_Island)

seinet_terms <- full_join(seinet_terms, Miguel_Is)
seinet_terms <- full_join(seinet_terms, Miguel_Island)

seinet_terms <- full_join(seinet_terms, Natividad_Island)

seinet_terms <- full_join(seinet_terms, Nicholas_Island)
seinet_terms <- full_join(seinet_terms, Nicolas_I)
seinet_terms <- full_join(seinet_terms, Nicolas_Island)

seinet_terms <- full_join(seinet_terms, Santa_Cruz_I)
seinet_terms <- full_join(seinet_terms, Santa_Cruz_Is)
seinet_terms <- full_join(seinet_terms, Santa_Cruz_Isl)
seinet_terms <- full_join(seinet_terms, Santa_Cruz_Islan)
seinet_terms <- full_join(seinet_terms, Santa_Cruz_Island)

seinet_terms <- full_join(seinet_terms, Santa_Rosa_I)
seinet_terms <- full_join(seinet_terms, Santa_Rosa_Is)
seinet_terms <- full_join(seinet_terms, Santa_Rosa_Isl)
seinet_terms <- full_join(seinet_terms, Santa_Rosa_Island)

seinet_terms <- full_join(seinet_terms, Todos_Santos_del)
seinet_terms <- full_join(seinet_terms, Todos_Santos_Island)

```

Voila, "seinet_terms" is a huge dataset and has everyone (but probably some dupes). 

# Importing WKT data

There are fewer WKT datasets, but we need to extact and glue them too. 
```{r unzip WKTs}
unzip("Data/Dec 2020/SEINet/WKTs/Barbara.zip", exdir = "Data/Dec 2020/SEINet/WKTs/Barbara")
unzip("Data/Dec 2020/SEINet/WKTs/Benito.zip", exdir = "Data/Dec 2020/SEINet/WKTs/Benito")
unzip("Data/Dec 2020/SEINet/WKTs/Catalina.zip", exdir = "Data/Dec 2020/SEINet/WKTs/Catalina")
unzip("Data/Dec 2020/SEINet/WKTs/Clemente.zip", exdir = "Data/Dec 2020/SEINet/WKTs/Clemente")
unzip("Data/Dec 2020/SEINet/WKTs/Coronados.zip", exdir = "Data/Dec 2020/SEINet/WKTs/Coronados")
unzip("Data/Dec 2020/SEINet/WKTs/Geronimo.zip", exdir = "Data/Dec 2020/SEINet/WKTs/Geronimo")
unzip("Data/Dec 2020/SEINet/WKTs/Guadalupe.zip", exdir = "Data/Dec 2020/SEINet/WKTs/Guadalupe")
unzip("Data/Dec 2020/SEINet/WKTs/Martin.zip", exdir = "Data/Dec 2020/SEINet/WKTs/Martin")
unzip("Data/Dec 2020/SEINet/WKTs/Miguel_Rosa_Cruz.zip", exdir = "Data/Dec 2020/SEINet/WKTs/Miguel_Rosa_Cruz")
unzip("Data/Dec 2020/SEINet/WKTs/Natividad_Cedros.zip", exdir = "Data/Dec 2020/SEINet/WKTs/Natividad_Cedros")
unzip("Data/Dec 2020/SEINet/WKTs/Nicolas.zip", exdir = "Data/Dec 2020/SEINet/WKTs/Nicolas")
unzip("Data/Dec 2020/SEINet/WKTs/Todos_Santos.zip", exdir = "Data/Dec 2020/SEINet/WKTs/Todos_Santos")
```

```{r import WKTs}
Barbara_WKT <- read_csv("Data/Dec 2020/SEINet/WKTs/Barbara/occurrences.csv", col_types = cols(.default = "c"))
Benito_WKT <- read_csv("Data/Dec 2020/SEINet/WKTs/Benito/occurrences.csv", col_types = cols(.default = "c"))
Catalina_WKT <- read_csv("Data/Dec 2020/SEINet/WKTs/Catalina/occurrences.csv", col_types = cols(.default = "c"))
Clemente_WKT <- read_csv("Data/Dec 2020/SEINet/WKTs/Clemente/occurrences.csv", col_types = cols(.default = "c"))
Coronados_WKT <- read_csv("Data/Dec 2020/SEINet/WKTs/Coronados/occurrences.csv", col_types = cols(.default = "c"))
Geronimo_WKT <- read_csv("Data/Dec 2020/SEINet/WKTs/Geronimo/occurrences.csv", col_types = cols(.default = "c"))
Guadalupe_WKT <- read_csv("Data/Dec 2020/SEINet/WKTs/Guadalupe/occurrences.csv", col_types = cols(.default = "c"))
Martin_WKT <- read_csv("Data/Dec 2020/SEINet/WKTs/Martin/occurrences.csv", col_types = cols(.default = "c"))
Miguel_Rosa_Cruz_WKT <- read_csv("Data/Dec 2020/SEINet/WKTs/Miguel_Rosa_Cruz/occurrences.csv", col_types = cols(.default = "c"))
Natividad_Cedros_WKT <- read_csv("Data/Dec 2020/SEINet/WKTs/Natividad_Cedros/occurrences.csv", col_types = cols(.default = "c"))
Nicolas_WKT <- read_csv("Data/Dec 2020/SEINet/WKTs/Nicolas/occurrences.csv", col_types = cols(.default = "c"))
Todos_Santos_WKT <- read_csv("Data/Dec 2020/SEINet/WKTs/Todos_Santos/occurrences.csv", col_types = cols(.default = "c"))
```

```{r glue WKTs}
seinet_wkts <- full_join(Barbara_WKT, Benito_WKT)
seinet_wkts <- full_join(seinet_wkts, Catalina_WKT)
seinet_wkts <- full_join(seinet_wkts, Clemente_WKT)
seinet_wkts <- full_join(seinet_wkts, Coronados_WKT)
seinet_wkts <- full_join(seinet_wkts, Geronimo_WKT)
seinet_wkts <- full_join(seinet_wkts, Guadalupe_WKT)
seinet_wkts <- full_join(seinet_wkts, Martin_WKT)
seinet_wkts <- full_join(seinet_wkts, Miguel_Rosa_Cruz_WKT)
seinet_wkts <- full_join(seinet_wkts, Natividad_Cedros_WKT)
seinet_wkts <- full_join(seinet_wkts, Nicolas_WKT)
seinet_wkts <- full_join(seinet_wkts, Todos_Santos_WKT)
```

# The final gluing

Now that we have both a seinet term and a seinet WKT dataset, we need to remove as many duplicates as we possibly can. 

Then, we'll refer this dataset against the CCH2 dataset!

```{r dupe clear}
seinet_all <- full_join(seinet_terms, seinet_wkts)
seinet_all_dist <- distinct(seinet_all, id, .keep_all = TRUE)
seinet_all_dist_2 <- distinct(seinet_all, occurrenceID, .keep_all = TRUE)

cch2 <- read_csv("Data/Dec 2020/CCH2/CCH_Clean.csv", col_types = cols(.default = "c"))

seinet_no_cch <- anti_join(seinet_all_dist_2, cch2, by = "id")
seinet_no_cch_2 <- anti_join(seinet_no_cch, cch2, by = "occurrenceID")

write.csv(seinet_no_cch_2, file = "Data/Dec 2020/SEINet/SEINet_Clean.csv", na="", row.names=FALSE)
```

